---
title: "mlr3 Basics"
author: "Matt Dube"
date: "9/29/2019"
output: 
    html_document:
      toc: true
      theme: flatly
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

## Setup

Load basic libraries and data. 

We'll be using the Employee Attrition dataset from the rsample package.

```{r setup_part_one}
library(ggplot2)
library(ggthemes)
library(data.table)

library(mlr3)
library(mlr3viz)

attrDT <- as.data.table(rsample::attrition)
```

## Setup Part 2
### review data

```{r setup_part_two}
attrDT[,1:5]

table(attrDT$Attrition)

```


The list of built-in learners (algorithms) is stored in the R6 dictionary mlr_learers.

```{r}
as.data.table(mlr_learners)
```

<br>
You can load additional learners using the <font face=bold color="red">mlr3learners</font> package.

```{r more_learners}
library(mlr3learners)

as.data.table(mlr_learners)[,.(key,predict_types,packages)]

```

<br>
This is a classification problem. We're going to next create a task and define a couple of learners.
<br>

```{r create_task}

tsk_attr <- TaskClassif$new(id="attrition", backend = attrDT, target = "Attrition")

tsk_attr
    
```

