---
title: "mlr3 Pipelines"
date: "9/29/2019 (updated: `r Sys.Date()`)"
output: 
    html_document:
      toc: true
      toc_float: true
      toc_depth: 4
      theme: flatly
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

```{r setup_part_one, echo = FALSE}

library(ggplot2)
library(ggthemes)
library(data.table)

library(mlr3)
library(mlr3learners)
library(mlr3tuning)
library(mlr3pipelines)
library(mlr3viz)

attrDT <- fread("../00_Data/attrition_train.csv")
attrDT[,Attrition := as.factor(Attrition)]

tsk_attr <- TaskClassif$new(id="attrition", backend = attrDT, 
                            target = "Attrition", positive = "Yes")

lrn_dummy  <- lrn("classif.featureless")
lrn_rpart  <- lrn("classif.rpart", predict_type = "prob")
lrn_ranger <- lrn("classif.ranger", predict_type = "prob")
lrn_log    <- lrn("classif.log_reg", predict_type = "prob")

msr_acc <- msr("classif.acc")
msr_auc <- msr("classif.auc")
```

# Pipelines Overview

## PipeOp
The most basic unit of functionality within `mlrpipelines` is the <stron>PipeOp</strong>.

The PipeOp represents a transformativeo operation on input leading to output.

PipeOps behave similar to functions, except  their behavior is determined by their `$state`

The mlr3 pipeline order and methodology has been carefully constructed to overcome shortcomings in common practices. 

The preprocessing methods (`pca`, `encode`, `impute`, `scale`, etc.) could be just be applied to training data and validation data separately, or they could be applied before resampling. 

This is not recommended because:

- preprocessing of each instance of prediction data (validation) should not depend on the remaining validation data.

- if preprocessing is performed before resampling is done, information about the test set can leak into the training set. Resampling should evaluate the <strong>generalization</strong> performance of the entire machine learning method.


```{r}
library(mlr3pipelines)

as.data.table(mlr_pipeops)[, .(key, input.num, output.num)][1:15]

```

